Online Verification of Commutativity

### 2020-08-11 acmPaper/paper.tex
Stub of related work

@@

% A diagram's structure can result in some redundancy, in the sense that equivalence of a subset of pairs can imply the equivalence of path pairs that aren't in the subset.
% For example, in Figure ~\ref{figure_redundancies}, verifying $p_1$ and $p_2$ implies that the paths in $p_3$ are equal too.

% \begin{figure}

% \begin{center}
% \begin{tikzpicture}[scale=0.2]
% \tikzstyle{every node}+=[inner sep=0pt]
% \draw [black] (12,-15.8) circle (3);
% \draw [black] (30.5,-30.5) circle (3);
% \draw [black] (46.4,-15.8) circle (3);
% \draw [black] (29.9,-15.8) circle (3);
% \draw [black] (15,-15.8) -- (26.9,-15.8);
% \fill [black] (26.9,-15.8) -- (26.1,-15.3) -- (26.1,-16.3);
% \draw (20.95,-16.3) node [below] {$f_1$};
% \draw [black] (14.35,-17.67) -- (28.15,-28.63);
% \fill [black] (28.15,-28.63) -- (27.84,-27.74) -- (27.21,-28.53);
% \draw (19.94,-23.64) node [below] {$g_1$};
% \draw [black] (29.063,-27.873) arc (-157.62406:-197.70132:13.638);
% \fill [black] (29.06,-27.87) -- (29.22,-26.94) -- (28.3,-27.32);
% \draw (27.49,-23.25) node [left] {$f_2$};
% \draw [black] (31.53,-18.309) arc (25.84176:-21.16715:11.992);
% \fill [black] (31.53,-18.31) -- (31.43,-19.25) -- (32.33,-18.81);
% \draw (33.28,-23.03) node [right] {$j_1$};
% \draw [black] (32.9,-15.8) -- (43.4,-15.8);
% \fill [black] (43.4,-15.8) -- (42.6,-15.3) -- (42.6,-16.3);
% \draw (38.15,-16.3) node [below] {$j_2$};
% \draw [black] (32.7,-28.46) -- (44.2,-17.84);
% \fill [black] (44.2,-17.84) -- (43.27,-18.01) -- (43.95,-18.75);
% \draw (39.77,-23.64) node [below] {$h_1$};
% \end{tikzpicture}

% $p_1$=($f_1;f_2$, $g_1$)\\
% $p_2$=($j_1;j_2$, $h_1$)\\
% $p_3$=($g_1;h_1$, $f_1;j_2$)
% \end{center}
% \caption{Path checking redundancies: verifying $p_1$ and $p_2$ implies that the paths in $p_3$ are equal.}
% \label{figure_redundancies}
% \end{figure}

@@

\xxx{Absolutely nothing related to this was ever done.}

>>>>

\label{sec:batchBaseline}

@@

@@

Section ~\ref{sec:batchBaseline} describes Murota's solution to efficiently finding the minimal set of path pairs that need to be compared to check if a given acyclic graph commutes ~\cite{commutative}.
We did not find any other work that solves the question of verifying that diagrams commute.

However, the question of commuting does come up in programming languages with implicit type conversion.
Gator ~\cite{gator}, as described in Section ~\ref{sec:gator}, supports automatic type conversion between geometry types.
The language implements some restrictions to eliminate obvious cases of non-commuting graphs, but does not verify that defined graphs commute, allowing scope for non-commuting graph definitions.
Frink ~\cite{frink} is a language that supports automatic conversion between units and infinite precision floating point numbers.
It does not appear to support the implicit definition of conversion between unites \xxx[AK]{Need to spend some time confirming this} but if extended to do so, would need to contend with the problem of commuting graphs.
The same is true for F\# which has support for units of measure ~\cite{unitsOfMeasure} and Ada's GNAT compiler~\cite{gnat}.

% Units of measure work resource: https://gmpreussner.com/research/dimensional-analysis-in-programming-languages
\section{Conclusion}
